### 2014-07-31 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits

Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) per kg of fuel consumed found from the SFPE Handbook~\cite{SFPE:Tewarson}. A balanced chemical reaction for wood combustion can written as:

@@

The value for the heat of combustion of wood used in this simulation was 16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}. The heat of combustion quantifies the amount of energy per unit mass of the fuel. The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:

@@

\chapter{Discussion}
The results of the FDS simulations will be discussed in two sections. The first section will address the results of the computational modeling as they relate to the interior hallways conditions. The second section will examine the the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.

>>>>

Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$). The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the SFPE Handbook~\cite{SFPE:Tewarson}. A balanced chemical reaction for wood combustion can written as:

@@

The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}. The heat of combustion quantifies the amount of energy per unit mass of the fuel. The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:

@@

\chapter{Discussion}
The results of the FDS simulations will be discussed in two sections. The first section will address the results of the computational modeling as they relate to the interior hallways conditions. The second section will examine the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
